### 2016-06-14 Manuscript/SW_early_life_telomeres_SOM.Rmd
More edits

```{r Table S2}
temp <- Loss

#Run the model
lm1 <- lmer(Loss ~ RTL+ Agemonths*(Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ) + (1|FieldPeriodID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm1 <- standardize(lm1)

>>>>

```{r Table S2}
temp <- dd3

#Run the model
lm1 <- glmer(DeltaRTLF ~ Agemonths+(Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ) + (1|FieldPeriodID) + (1|TerritoryID),
            data = temp,
            family = 'binomial',
            REML = FALSE)
lm1 <- standardize(lm1)

### 2016-06-14 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More edits

**Figure 4** Longitudinal telomere dynamics in juvenile Seychelles warblers. **A** Juvenile telomere length in relation to adult telomere length measured in the same individual. **B** $\Delta$RTL in relation to the time between sampling events. Lines and shaded areas represent fitted values and 95% confidence limits from general linear models. Raw data have been ommited from **B** for the sake of clarity, but are plotted in Figure S1.

**Figure 5** Factors affecting $\Delta$RTL in juvenile Seychelles warblers. **A** Model averaged estimates and 95% confidence intervals for explanatory terms used in a linear mixed model with $\Delta$RTL as the response variable (see main text for details; TQ = territory quality). **B** $\Delta$RTL in relation to tarsus length and sex.

@@

temp <- juv
temp$LayYear <- factor(temp$LayYear)

@@

temp <- juv

@@

temp <- juv

@@

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1,
           col = LossF)) +
  ylab('Adult RTL') + 
  xlab('Juvenile RTL') +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  geom_point()+
  scale_colour_manual(values = c('navy','red'))+
  annotate('text',x = 0,y = 3,label = 'A')

@@

temp <- Loss

Fig4D <- ggplot(temp,aes(col=LossF,y = Loss,x = TimeDiff))+
    geom_point()+
  theme_classic()+
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
  ylim(c(-2,2))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('navy','red'))+
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 2,label = 'D')

@@

>>>>

**Figure 4** Longitudinal telomere dynamics in subset(dd,Agemonths<12)enile Seychelles warblers. **A** subset(dd,Agemonths<12)enile telomere length in relation to adult telomere length measured in the same individual. **B** $\Delta$RTL in relation to the time between sampling events. Lines and shaded areas represent fitted values and 95% confidence limits from general linear models. Raw data have been ommited from **B** for the sake of clarity, but are plotted in Figure S1.

**Figure 5** Factors affecting $\Delta$RTL in subset(dd,Agemonths<12)enile Seychelles warblers. **A** Model averaged estimates and 95% confidence intervals for explanatory terms used in a linear mixed model with $\Delta$RTL as the response variable (see main text for details; TQ = territory quality). **B** $\Delta$RTL in relation to tarsus length and sex.

@@

temp <- subset(dd,Agemonths<12)
temp$LayYear <- factor(temp$LayYear)

@@

@@

temp <- subset(dd,Agemonths<12)

@@

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1,
           col = LossF)) +
  ylab('Adult RTL') + 
  xlab('subset(dd,Agemonths<12)enile RTL') +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  geom_point()+
  scale_colour_manual(values = c('navy','red'))+
  annotate('text',x = 0,y = 3,label = 'A')

@@

temp <- dd3

Fig4D <- ggplot(temp,aes(col=DeltaRTLF,y = DeltaRTL,x = TimeDiff))+
    geom_point()+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
  ylim(c(-2,2))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('navy','red'))+
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 2,label = 'D')

@@

temp <- with(dd3,tapply(DeltaRTL,Agemonths,mean))
tempSE <- with(dd3,tapply(DeltaRTL,Agemonths,se))*1.96

plot(temp~names(temp),type = 'l',ylim = c(-0.8,0.8))
points(temp+tempSE~names(temp),type = 'l',lty = 2)
points(temp-tempSE~names(temp),type = 'l',lty = 2)
abline(0,0,col = 'red',lwd = 2)

plot(DeltaRTL~TimeDiff,data = dd3)
